% Adapted from layout by Jake VanderPlas
%  https://staff.washington.edu/jakevdp/
%

\documentclass{article} %{{{--

\usepackage[paper=a4paper,
	    top=2cm,
	    left=1.35cm,
	    width=18.2cm,
	    bottom=2cm
	    ]{geometry}
            %margin=4cm,

\usepackage{calc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{color,hyperref}
\usepackage{graphicx}
\usepackage{multicol}

\usepackage{wasysym} % For phone symbol
\usepackage{url}

\def\bf{\bfseries}
\def\sf{\sffamily}
\def\sl{\slshape}
% Semi condensed bold

\definecolor{deep_blue}{rgb}{0,.2,.5}
\definecolor{dark_blue}{rgb}{0,.1,.3}
\definecolor{myblue}{rgb}{.01,0.21,0.71}
\definecolor{gray}{rgb}{.5, .5, .5}

\hypersetup{pdftex,  % needed for pdflatex
  breaklinks=true,  % so long urls are correctly broken across lines
  colorlinks=true,
  urlcolor=myblue,
  %linkcolor=darkblue,
  %citecolor=darkgreen,
  }


%% This gives us fun enumeration environments.
\usepackage{enumitem}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% Reference the last page in the page number
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
%\fancyfootoffset{\marginparsep}+\marginparwidth}
\lfoot{
  \hspace{-2\marginparsep}
  \,\hfill \arabic{page} of \protect\pageref*{LastPage}  \hfill \,\\
  \,\hfill {\footnotesize \textcolor{gray}{updated January 2017~~~~~}} \hfill\,
}

\newcommand{\mydate}[1]{{\textcolor{gray}{\footnotesize #1}}}


\newcommand{\makeheading}[1]%
        {%\hspace*{-\marginparsep minus \marginparwidth}%
         %\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
         \begin{minipage}[t]{\textwidth}%
                {\Large #1}\\%[-0.5\baselineskip]%
                \vskip 0.2\baselineskip
                 \color{deep_blue}{\rule{\columnwidth}{3pt}}%
         \end{minipage}
	 \vskip 1.\baselineskip plus 2\baselineskip minus 1.\baselineskip
	}

\newlength\sidebarwidth
\setlength\sidebarwidth{3.6cm}

\newcommand{\topic}[3][]%
	 {\pagebreak[2]%
	 \vskip 1.5\baselineskip plus 3\baselineskip minus 0.7\baselineskip
	 \begin{minipage}{\textwidth}
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft \bf\sf
	 \color{deep_blue}{\Large #2}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 \nopagebreak{\color{deep_blue}%
		    \rule{0pt}{\baselineskip}%
		    \rule{\linewidth}{2.5pt}%
		    \llap{\raisebox{.3\baselineskip}{\sf #1}}%
		    \vspace*{.1\baselineskip}%
		    }%
	 #3%
	 \end{minipage}
	 \end{minipage}}

\newcommand{\smalltopic}[2]%
	 {\pagebreak[2]%
	 \vskip 1\baselineskip plus 2\baselineskip minus 0.3\baselineskip
	 \begin{minipage}{\textwidth}
	 %\hspace{-\marginparsep minus \marginparwidth}%
         \phantomsection\addcontentsline{toc}{subsection}{#1}%
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft \bf\sf %\vskip -0.5\baselineskip
	 \textcolor{dark_blue}{\large #1}%
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 \nopagebreak{%
	    %\vspace{-.7\baselineskip}%
	    \rule{\linewidth}{.5pt}%
	    \vspace{.1\baselineskip}%
	    }%
	    #2
	 \end{minipage}
	 \end{minipage}}

\newcommand{\subtopic}[3][]
	 {\begin{minipage}{\textwidth}
	 \vspace*{.4\baselineskip}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
	 % Super posh: using semi-bold condensed fonts. Works only with
	 % lmodern
         \raggedleft {\sf\fontseries{sbc}\selectfont #2}
	 %{\small\sl\\[-0.2\baselineskip] #1}
         {\\[-0.2\baselineskip] \textcolor{gray}{\footnotesize #1}}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #3%
	 \end{minipage}%
	 \vspace*{.2\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

\newcommand{\dateonly}[2][]
	 {\begin{minipage}{\textwidth}
	 \vspace*{.4\baselineskip}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft {~}
         {\\[-\baselineskip] \textcolor{myblue}{\footnotesize #1}}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #2%
	 \end{minipage}%
	 \vspace*{.2\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

\newcommand{\sidenote}[2]
	 {\vspace*{-.2\baselineskip}\begin{minipage}{\textwidth}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft {#1}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #2%
	 \end{minipage}%
	 \vspace*{.5\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

% New lists environments
\newlist{outerlist}{itemize}{1}
\setlist[outerlist]{font=\sffamily\bfseries, label=\textbullet}
\setitemize{topsep=0ex, partopsep=0ex}
\setdescription{font=\normalfont\sffamily\bfseries, itemsep=.5ex,
    parsep=.5ex, leftmargin=3ex}

\newcommand{\blankline}{\quad\pagebreak[2]}

\def\mydot{\textcolor{deep_blue}{\rule{1ex}{1ex}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%--}}}%
\begin{document}
\makeheading{
\begin{minipage}[B]{0.5\textwidth}
    %\vfill
    %\vspace*{-.5\baselineskip}%
    \parbox{15cm}{
	%\hskip -0.1cm
	{\Huge\bf\sf \color{deep_blue} D\huge \hskip -0.05cm ANIEL \Huge P. \Huge R\huge \hskip -0.05cm USSO}
	%\\[-.1\baselineskip]

    }
\end{minipage}
\begin{minipage}[B]{8cm}
    \raggedleft
    \,\vskip -1em
    \small
        www.danielprusso.com\\
        @russodanielp\\
        github.com/russodanielp\\
	{\texttt {russodanielp@gmail.com}}\\%
	609.221.9928
    \vspace*{-.5\baselineskip}%
\end{minipage}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Current research interests include developing predictive models to be used in pharmacology and toxicology. Specifically, how the "Big Data" landscape can be exploited to aid in chemical risk assessment and identification of drug candidates.
Very passionate about scientific communication/teaching and inspired by scientists who discuss research in a clear, accessible manner. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{E \large\hskip -1ex DUCATION}{~}

    \subtopic[2014-2018 (Expected)]{\bf PhD}{
        Computational \& Integrative Biology, Rutgers University, Camden, NJ\\
        Advised by Dr. Hao Zhu\\
				Thesis: \textit{The Chemical In-vitro, In-vivo Profiling Project}\\
				May, 2018: Expected Graduation\\
				March, 2016: Passed Qualifying Exam with Distinction\\
				May, 2015: Completed Coursework, GPA: 3.96
    }

    \subtopic[2011-2014]{\bf MS}{
      Biology, Rutgers University, Camden, NJ\\
      Advised by Dr. Hao Zhu\\
			Thesis: \textit{Quantitative Structure-Activity Modeling
			of 5-Hydroxytryptamine \\
			Type-6 Receptor Antagonists}\\
			March, 2014: Passed Thesis Defense with Distinction\\
			May, 2013: Completed Coursework, GPA: 4.00
    }

    \subtopic[2004-2009]{\bf BA}{
      Biology, Rutgers University, Camden, NJ\\
    }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{E \large\hskip -1ex XPERIENCE}{~}

\vspace*{-0.5\baselineskip}
\smalltopic{Employment}{}

    \subtopic[2014-Present]{Rutgers University\\Camden, NJ}{
    		           \textit{Teaching/Graduate Assistant}\\
			Perform cheminformatics research in the lab of Dr. Hao Zhu. Develop Statistical and Machine Learning models for toxicity.
			Lecture and grade students in courses related to Biology, Biochemistry, and Computer Science.   
    }

    \subtopic[2013-2014]{West-Ward Pharmaceuticals\\Cherry Hill, NJ}{
    		           \textit{Microbiologist}\\
			Validated and performed experiments in the detection of microbial
			isolates and endotoxins from drug product and environmentally
			controlled manufacturing areas.  Performed testing and recording
			in compliance with SOPs and cGMP regulations under FDA discretion.
    }

    \subtopic[2012-2013]{Rutgers University\\Camden, NJ}{
      			\textit{Part-time Lecturer/Certified College Reading \& Learning Association Tutor}\\
			Lectured, graded, and tutored a variety of undergraduate level science courses in the
			fields of Biology, Biochemistry and Chemistry.
    }

    \subtopic[2008-2012]{Adventure Aquarium\\Camden, NJ}{
      			\textit{Biologist}\\
			Oversaw daily husbandry and animal health operations for a variety
			of marine, fresh, and brackish water fish and invertebrates.  Assisted in
		          diving and animal health operations for the 700,000-gallon Ocean
		          Realm and 500,000-gallon Shark Realm exhibits featuring sharks, rays,
			turtles, and other large sea life.  Educated visitors in marine science
			through guided tours and daily guest interactions.
    }

\smalltopic{Leadership Experience}{}

    	\subtopic[2016-Present]{Graduate Student Advisory Council}{
			\textit{Council Member}\\
      			Represent the interests of the Rutgers-Camden Graduate Students
			during meetings as part of an advisory group
			to the Associate Dean and Assistant Dean of the Graduate School.
			Assist with student orientation, open houses, and other graduate
			school programs.
    }

    	\subtopic[2015-Present]{Center for Computational \&
		                        Integrative Biology Journal Club}{
			\textit{Founder, Organizer}\\
		 	Organize social and academic events for the students of The Rutgers Center
			for Computational \& Integrative Biology.  Select current and relevant papers
			in Computational Biology and assemble weekly meetings for discussion.  
			Invite, host, and organize polling for student-elected seminar speakers.
    }

	\subtopic[2015]{The Journal of Biological Sciences at Rutgers-Camden}{
			 \textit{Student Editor}\\
			Helped students prepare manuscripts for submission to faculty-reviewed scientific journal showcasing 
			exceptional undergraduate research.  Worked with both students and the editor-in-chief to address 
			reviewer comments and finalize manuscripts for print.   
}

\smalltopic{Community Involvement}{}

	\subtopic[2016-Present]{Software Carpentry}{
		     \textit{Instructor}\\
		      Organize and host Software Carpentry workshops which aim to teach and
 		     describe a set of best practices for scientific software development that have
		     solid foundations in research and experience.
		    }

	\subtopic[2010-2013]{The Academy of Natural Sciences\\Philadelphia, PA}{
                         \textit{Ichthyology Volunteer}\\
		    Organized and curated the Ichthyology Collection consisting of close to
		   1.2 million catalogued specimens.  Collected radiographic images (X-ray) of type
		   specimens.  Prepared and edited images using Adobe Photoshop.
		    }

	\subtopic[2005-2008]{Adventure Aquarium\\Camden, NJ}{
		    \textit{Fish \& Invertebrates Volunteer}\\
		    Assisted biology staff in daily husbandry and animal health operations for a variety
		    of marine, fresh, and brackish fish and invertebrates.
		    }

\smalltopic{Teaching Experience}{\\All courses were taught at \textbf{Rutgers University}, Camden, NJ.\\  "Guest Lectures" are individual classes.  }

    \subtopic{50:198:111}{Programming Fundamentals Lab}
    \subtopic{50:198:113}{Object-Oriented Programming Recitation}
    \subtopic{50:120:295}{Principals and Practices of Biological Research}
    \subtopic{50:120:308}{Genetics Lab}
    \subtopic{50:160:339}{Organic Chemistry Lab}
    \subtopic{50:120:212}{Microbiology and Its Applications Lab}
    \subtopic{50:120:107}{General Biology Lab}
    \subtopic{56:115:511}{Biochemistry I, \textit{Guest Lecturer}: "Drug Discovery",  "Sugars and Polysaccharides", "Protein Structures", "Aqueous Solutions", "Acids and Bases"}
    \subtopic{56:121:555}{Cheminformatics, \textit{Guest Lecturer}: "PubChem: Ushering Chemistry into 'Big Data'"}

\smalltopic{Professional Membership}{}

    	\subtopic{2017-Present}{Society of Toxicology (Application Pending Approval)}
    	\subtopic{2015-Present}{American Chemical Society}

    

\smalltopic{Certifications}{}

    	\subtopic{2016}{Software Carpentry Instructor}
    	\subtopic{2012}{College Reading \& Learning Association Tutor}
	\subtopic{2011}{PADI Advanced Open Water Diver}
	\subtopic{2010}{PADI Open Water Diver Certification}
    


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\topic{R \large\hskip -1ex ESEARCH\\
	 S \large\hskip -1ex KILLS}{}

\smalltopic{Computational}{

  \begin{itemize}[leftmargin=0ex, itemsep=0ex, labelindent=-2ex, parsep=.5ex]
    \item[\mydot] Very good working knowledge of Python and Object-Oriented Design specializing in scientific computing,
			specifically in the field of cheminformatics.
    \item[\mydot] Very good working knowledge of data science and data visualization using the Python packages Pandas,
			Numpy, SciPy, scikit-learn, matplotlib, and Bokeh.
    \item[\mydot] Proficient in Machine Learning principles and practices and their application to chemistry, toxicology,
			and early stage drug discovery.
    \item[\mydot] Experience with a variety of computer tools and languages including bash, Git, Markdown, HTML, \LaTeX{},
			MongoDB, SQL, and web development using Flask.  
    \item[\mydot] Very passionate about scientific communication and education.  Host a blog titled \href{www.danielprusso.com}{"Drug Discovery in Python"}
			showcasing data visualization and analysis within Python using chemistry and baseball as motivating fields.
  \end{itemize}

}

\smalltopic{Experimental}{

  \begin{itemize}[leftmargin=0ex, itemsep=0ex, labelindent=-2ex, parsep=.5ex]
    \item[\mydot] Good experience with bacterial cell culture and aseptic technique with a strong focus on isolation and
			identification of bacteria and bacterial endotoxins.  
    \item[\mydot] Experience with human cell culture (Hep G2) and assays.   
    \item[\mydot] Good experience with a variety of biology and chemistry lab equipment and techniques including microscopy, high-pressure liquid
			chromatography, electrophoresis, DNA/RNA extraction, media buffer preparation, and various wet chemistry tests (pH,
			alkalinity, titrations).
    \item[\mydot] Good experience with fresh and marine fish and invertebrate care with a focus on the culture of various seahorse species: \textit{H. erectus}, \textit{H. reidi},
			 \textit{H. abdominalis}, and \textit{H. zosterae}.
  \end{itemize}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{P \large\hskip -1ex ROJECTS \& \\
	A \large\hskip -1ex PPLICATIONS }{~}

    	\subtopic[2015-Present]{CIIPro}{I am co-creator, developer, and maintainer of the \textit{The Chemical In-vitro, In-vivo Profiling Project (CIIPro)}.  CIIPro is an online cheminformatics web 
				portal designed for large scale chemical and biological data analysis.  CIIPro aims to harmonize the immense amount of data available in disparate public repositories for inclusion in 
				cheminformatic studies.  Written in Python and powered by Flask, CIIPro is available at \href{ciipro.rutgers.edu}{ciipro.rutgers.edu}}.  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{F \large\hskip -1ex UNDING }{~}

    	\subtopic{Feb 2017}{Center for Computational and Integrative Biology Travel Grant.  \$500.00 }
    	\subtopic{Feb 2017}{Dean’s Graduate Conference Travel Grant.  \$500.00  }
	\subtopic{June 2016}{Teaching Assistant and Graduate Assistant Professional Development Fund Award.  \$700.00 }
	\subtopic{Jan 2010}{Dean's Tuition Remission Award, Biology Department.  \$1,000.00}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\topic{P \large\hskip -1ex UBLICATIONS \\
	\& T \large\hskip -1ex ALKS}{~}

\newcounter{BookNumber}
\newcommand{\book}{\item[{\bf \textcolor{myblue}{[\stepcounter{BookNumber}\arabic{BookNumber}]}}]}

\smalltopic{Book Chapters}{
  \begin{itemize}[leftmargin=0ex, itemsep=0ex, labelindent=-4ex, parsep=.5ex]

    \book \textbf{Russo D P} and Zhu H. Accessing the High-Throughput Screening Data Landscape. In: \textit{High-Throughput Screening Assays in Toxicology}
	(by Zhu, H and Xia, M; Editors) Chapter 16, pgs. 153-159. Springer New York, 2015. ISBN: 978-1-4939-6344-7.

  \end{itemize}
}

\newcounter{ArticleNumber}
\newcommand{\article}{\item[{\bf \textcolor{myblue}{[\stepcounter{ArticleNumber}\arabic{ArticleNumber}]}}]}
\smalltopic{Articles}{
  \begin{itemize}[leftmargin=0ex, itemsep=0ex, labelindent=-4ex, parsep=.5ex]
    \article \textbf{Russo D P}, Kim M T, Wang W, Pinolini D, Shende S, Zhu H. \textit{CIIPro: a new read-across portal to fill data gaps using public large-scale chemical and biological data}. Bioinformatics. (2016); doi: 10.1093/bioinformatics/btw640  
    \article Xiang J, Zhang Z, Mu Y, Xu X, Guo S, Liu Y, \textbf{Russo D P}, Zhu H, Yan B, Bai X. \textit{Discovery of novel tricyclic thiazepine derivatives as anti-drug-resistant cancer agents by combining diversity-oriented synthesis and converging 
	screening approach}. ACS Combinatorial Science. (2016); doi: 10.1021/acscombsci.6b00010
    \article Yan B, Mu Y, Liu Y, Xiang J, Zhang Q, Zhai S, \textbf{Russo D P}, Zhu H, Bai X. \textit{From fighting depression to conquering tumors: a novel tricyclic thiazepine compound as a tubulin polymerization inhibitor}. 
	Cell Death and Disease. (2016) 7, e2143; doi:10.1038/cddis.2016.53  
    \article Ball N, Cronin M T, Shen J, Adenuga M D, Blackburn K, Booth E D, Bouhifd M, Donley E, Egnash L, Freeman J J, Hastings C, Juberg D R, Kleensang A, Kleinstreuer N, Kroese E D, Luechtefeld T, Maertens A, Marty S, Naciff J M, Palmer J, Pamies D,
           Penman M, Richarz A N, \textbf{Russo D P}, Stuard S B, Patlewicz G, van Ravenzwaay B, Wu S, Zhu H, Hartung T. \textit{Toward Good Read-Across Practice (GRAP) guidance}. ALTEX. (2015) 33, 149-166. \textbf{(Featured together with the following 
	4 ALTEX papers in Science Feb 12, 2016 “A crystal ball for chemical safety” and Nature Feb 11, 2016 “Legal tussle delays launch of huge toxicity database”)}
     \article Luechtefeld T, Maertens A, \textbf{Russo D P}, Rovida C, Zhu H, Hartung T. \textit{Analysis of publicly available skin sensitization data from REACH registrations 2008-2014}. ALTEX. (2015) 33, 135-148.
     \article Luechtefeld T, Maertens A, \textbf{Russo D P}, Rovida C, Zhu H, Hartung T. \textit{Analysis of Draize eye irritation testing and its prediction by mining publicly available 2008-2014 REACH data}. ALTEX. (2015) 33, 123-134.
     \article Luechtefeld T, Maertens A, \textbf{Russo D P}, Rovida C, Zhu H, Hartung T. \textit{Analysis of public oral toxicity data from REACH registrations 2008-2014}. ALTEX. (2015) 33, 111-122.
     \article Luechtefeld T, Maertens A, \textbf{Russo D P}, Rovida C, Zhu H, Hartung T. \textit{Global analysis of publicly available safety data for 9,801 substances registered under REACH from 2008-2014}. ALTEX. (2015) 33, 95-109.  
     \article Kotchoni, S O, Noumavo, P A, Adjanohoun A, \textbf{Russo D P}, Dell Angelo J, Gachomo E W, Baba-Moussa L. \textit{A simple and efficient seed-based approach to induce callus production from B73 maize genotype}. American Journal of Molecular Biology. (2012) 2, 380-385.   ]	
	
  \end{itemize}
}




\smalltopic{Presentations}{}

    \dateonly[Sept 2016]{\textit{CIIProCluster: Developing enhanced predictive toxicity models using big data}. \\
						Center for Computational and Integrative Biology Fall Seminar, Camden, NJ}
    \dateonly[Sept 2015]{\textit{CIIPro:  An online cheminformatics portal for large scale chemical data analysis}. \\
						Center for Computational and Integrative Biology Fall Seminar, Camden, NJ}
    \dateonly[Aug 2015]{\textit{CIIPro:  An online cheminformatics portal for large scale chemical data analysis}. \\
						American Chemical Society Annual Meeting - Division of Chemical Information, Boston, MA}
    \dateonly[May 2013]{\textit{Quantitative structure activity relationship modeling of serotonin type-6 receptor antagonists}. \\
						Rutgers-Camden Biology Spring Seminar, Camden, NJ}

\smalltopic{Posters}{\small \\{\textcolor{myblue}{\it $**$ poster presenter}}}

    \dateonly[**Dec 2016]{\textbf{Russo D P}, Wang W, Strickland J, Shende S, Zhu H. \textit{CIIProCluster: Developing Read-Across Predictive Toxicity Models Using Big Data}.
				 Center for Computational and Integrative Biology Annual Retreat, Camden, NJ}
    \dateonly[Mar 2016]{Wang W, \textbf{Russo D P}, Kim M, Zhao L, Huang R, Xia M, Hartung, T, Zhu H. \textit{Profiling and Evaluating Environmental Chemicals that Induce Oral Acute Toxicity Using Mitochondrial
				Membrane Potential Disruption Assay, Big Data and New Read-across Strategy}. Society of Toxicology 55th Annual Meeting, New Orleans, LA}
    \dateonly[**Sep 2015]{\textbf{Russo D P}, Wang W, Kim M T, Pinolini D, Zhu H. \textit{CIIPro:  An online cheminformatics portal for large scale chemical data analysis}. 
				Center for Computational and Integrative Biology Annual Retreat, Camden, NJ}
    \dateonly[**Aug 2015]{\textbf{Russo D P}, Wang W, Kim M T, Pinolini D, Zhu H. \textit{CIIPro:  An online cheminformatics portal for large scale chemical data analysis}. 
				Sci-Mix Poster Session, American Chemical Society - Division of Chemical Information, Boston, MA}
    \dateonly[Sept 2013]{Kim T M, Lallier B, Zhang J, \textbf{Russo D P}, Mayer-Bacon C, Boison A, Kotchoni S O, Martin J V, Zhu H. \textit{Computational profiling of the binding mechanisms of GAPAA receptor ligands}.
				American Chemical Society Annual Meeting- Division of Chemical Information, Indianapolis, IN}

\smalltopic{Workshops \& Panels}{}

    \dateonly[Nov 2016]{\textit{Organizer \& Host}, Software Carpentry Workshop - Rutgers University, Camden NJ}
    \dateonly[Mar 2016]{\textit{Panelist}, Admitted Students Day Panel - Rutgers University, Camden NJ}
    \dateonly[Oct 2016]{\textit{Panelist}, Good Read-Across Practices Workshop - Johns Hopkins Center for Alternatives to Animal Testing, Baltimore, MD}


\end{document}
